Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-24 paper/paper.tex
Clean up/merge old scenarios text with experimental parameters section

@@

\subsection{Experimental Parameters}
\label{sec:exp-parameters}
\TODO{Edit this first paragraph, which was moved from the old Scenarios section}

We have prepared test scenarios to evaluate the proposed algorithms under a
range of parameters that enables us to observe the interesting characteristics
of the different algorithms for smaller and larger constraints. For a given
ensemble we can expect, in general, that the amount of work done (in terms of
workflows completed) depends mainly on the budget constraint, which determines
the number of machine-hours that can be provisioned. The deadline, although
important in terms of scheduling, is assumed to be greater than the longest critical
path of all workflows in the ensemble. We can then have a trivial but unrealistic solution
where the deadline  is long enough to allow all the workflow tasks to be
executed sequentially: this eliminates all the overheads of parallel execution
and leads to the highest resource utilization. More interesting and more
realistic, however, are the cases where the deadline is shorter than the serial
schedule, since it forces the system to provision multiple VMs to execute
workflow tasks in parallel.

For each application, we selected ranges of constraints (deadline and budget) to cover a broad parameter space: from tight constraints, where only a small number of workflows can be completed, to more liberal constraints where all, or almost all, of the workflows can be completed. These parameters vary among the applications and ensemble types and sizes. The budget constraints for each ensemble are calculated by identifying the smallest budget required to execute one of the workflows in the ensemble (MinBudget), and the smallest budget required to execute all workflows in the ensemble (MaxBudget): 
%
$$
MinBudget = \min_{w\ \in\ e}{Cost(w)}
$$
$$
MaxBudget = \sum_{w\ \in\ e}{Cost(w)}
$$
%
This range---$[MinBudget, MaxBudget]$---is then divided into equal intervals to determine the budgets to use in each experiment. Similarly, the deadline constraints for each ensemble are calculated by identifying the smallest amount of time required to execute a single workflow in the ensemble (MinDeadline), which is the length of the critical path for the workflow with the shortest critical path, and by identifying the smallest amount of time required to execute all workflows (MaxDeadline), which is the sum of the critical paths of all the workflows:
%
$$
MinDeadline = \min_{w\ \in\ e}{CriticalPath(w)}
$$
$$
MaxDeadline = \sum_{w\ \in\ e}{CriticalPath(w)}
$$
%
This range---$[MinDeadline, MaxDeadline]$---is then divided into equal intervals to determine the deadlines to use in each experiment. By computing the budget and deadline constraits in this way we ensure that the experiments for each ensemble cover the most interesting area of the parameter space for the ensemble.

>>>>

\subsection{Experimental Parameters}
\label{sec:exp-parameters}

In order to observe the interesting characteristics of the proposed algorithms, we evaluated them using a broad range of constraint values. For each ensemble, we selected ranges for deadline and budget that cover a broad parameter space: from tight constraints, where only a small number of workflows can be completed, to more liberal constraints where all, or almost all, of the workflows can be completed. Because the interesting parameter space varies among the applications, ensemble types and sizes, we computed constraint ranges based on the characteristics of each ensemble. The budget constraints are calculated by identifying the smallest budget required to execute one of the workflows in the ensemble (MinBudget), and the smallest budget required to execute all workflows in the ensemble (MaxBudget): 
%
$$
MinBudget = \min_{w\ \in\ e}{Cost(w)}
$$
$$
MaxBudget = \sum_{w\ \in\ e}{Cost(w)}
$$
%
This range---$[MinBudget, MaxBudget]$---is then divided into equal intervals to determine the budgets to use in each experiment. Similarly, the deadline constraints for each ensemble are calculated by identifying the smallest amount of time required to execute a single workflow in the ensemble (MinDeadline), which is the length of the critical path for the workflow with the shortest critical path, and by identifying the smallest amount of time required to execute all workflows (MaxDeadline), which is the sum of the critical paths of all the workflows:
%
$$
MinDeadline = \min_{w\ \in\ e}{CriticalPath(w)}
$$
$$
MaxDeadline = \sum_{w\ \in\ e}{CriticalPath(w)}
$$
%
This range---$[MinDeadline, MaxDeadline]$---is then divided into equal intervals to determine the deadlines to use in each experiment. By computing the budget and deadline constraits in this way we ensure that the experiments for each ensemble cover the most interesting area of the parameter space for the ensemble.

@@
